---
title: "LI6800 output analysis"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    social: NULL
    source_code: NULL
    self_contained: TRUE
    theme: sandstone
runtime: shiny
---

```{r CHECK_LIBRARIES, message=FALSE, include=FALSE}
source("Required_libraries.R")
```

```{r DATA _SELECTION, message=FALSE, include=FALSE}
selected_file <- file.choose()
header_lines <- readLines(selected_file, n = 62)
data <- as.data.frame(read.delim(selected_file, header = FALSE, sep = "\t", skip = 64, fill = TRUE))
colnames(data) <- paste(data[1,])
data <- data[-c(1,2),]
data <- data[, -c(2,4,5,6,7)]
data[] <- lapply(data, as.numeric)
```

Main_graph
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r X_AXIS, message=FALSE}
selectInput('xcol1', 
            HTML('<span style="font-size: 16px;"><b>X  Axis Variable</b></span>'), 
            names(data))

sliderInput('xmin', 'X Min Value', min = min(data[[1]]), max = max(data[[1]]), value = min(data[[1]]))
sliderInput('xmax', 'X Max Value', min = min(data[[1]]), max = max(data[[1]]), value = max(data[[1]]))


observeEvent(input$xcol1, {
  updateSliderInput(session, 'xmin', 'X Min Value',
                    min = min(data[[input$xcol1]]),
                    max = max(data[[input$xcol1]]),
                    value = min(data[[input$xcol1]]))

  updateSliderInput(session, 'xmax', 'X Max Value',
                    min = min(data[[input$xcol1]]),
                    max = max(data[[input$xcol1]]),
                    value = max(data[[input$xcol1]]))
})
```

```{r Y_AXIS, message=FALSE}
    
selectInput('ycol1', 
            HTML('<span style="font-size: 16px;"><b>Y  Axis Variable</b></span>'), 
            names(data),
            selected=names(data)[[3]])

sliderInput('ymin', 'Y Min Value', min = min(data[[3]]), max = max(data[[3]]), value = min(data[[3]]))
sliderInput('ymax', 'Y Max Value', min = min(data[[3]]), max = max(data[[3]]), value = max(data[[3]]))


observeEvent(input$ycol1, {
  updateSliderInput(session, 'ymin', 'Y Min Value',
                    min = min(data[[input$ycol1]]),
                    max = max(data[[input$ycol1]]),
                    value = min(data[[input$ycol1]]))

  updateSliderInput(session, 'ymax', 'Y Max Value',
                    min = min(data[[input$ycol1]]),
                    max = max(data[[input$ycol1]]),
                    value = max(data[[input$ycol1]]))
})

```

Column
-----------------------------------------------------------------------

```{r GRAPH, message=FALSE}
selectedData1 <- reactive(
  data[, c(input$xcol1, input$ycol1)],
)

renderPlotly({
  par(mar = c(5.1, 4.1, 0, 1))
  p <- ggplot(selectedData1(), aes_string(x=input$xcol1, y=input$ycol1)) +
    geom_point(shape=20) +
    theme_bw() +
    ylim(input$ymin, input$ymax) +
    xlim(input$xmin, input$xmax)
  
  ggplotly(p)
       })
```

If you want to download only the data used to generate this graph, press on the "Download" button below.
```{r DOWNLOAD_DATA, message=FALSE}
downloadHandler(
  filename = function() {
      filename <- input$file$name
      paste(input$xcol1, input$ycol1, ".csv", sep = "_")
  },
  content = function(file) {
    data <- selectedData1()
    write.csv(data, file, row.names = FALSE)
  }
)

uiOutput("downloadButton")

```

```{r EXTRACT_DATA, message=FALSE}
column_selector <- selectInput(
  inputId = "columns",
  label = "If you want to extract specific columns of your data file:",
  choices = colnames(data),
  selected = NULL,
  multiple = TRUE  
)

output$exported_data <- downloadHandler(
  filename = function() {
    paste("exported_data_", Sys.Date(), ".csv", sep = "")
  },
  content = function(file) {
    selected_data <- data[, input$columns, drop = FALSE]
    write.csv(selected_data, file, row.names = FALSE, sep = ",")
  }
)

tabPanel("Export Data",
         column(6,
                h3("Export Data"),
                column_selector,
                downloadButton("exported_data", "Download")
         )
)

```


Informations
=======================================================================

This part contains the header of your data. Important information to keep.

<div style="overflow-y: scroll; max-height: 300px;">
```{r HEADER, message=FALSE}
print(header_lines)

```
</div>

Controls
=======================================================================

Row
-----------------------------------------------------------------------
<!-- TEMPERATURE -->
```{r message=FALSE}

palette <- brewer.pal(length(unique(data$CategoryVariable)), "Set1")

renderPlotly({
  par(mar = c(5.1, 4.1, 0, 1))
  p <- ggplot(data) +
    geom_point(aes_string(x = input$xcol1, y = data$TleafEB, color = "'TleafEB'"), shape = 20) +
    geom_point(aes_string(x = input$xcol1, y = data$TleafCnd, color = "'TleafCnd'"), shape = 20) +
    geom_point(aes_string(x = input$xcol1, y = data$Tair, color = "'Tair'"), shape = 20) +
    theme_bw() +
    xlim(input$xmin, input$xmax) +
    ylab("Temperature (°C)")

  p <- ggplotly(p)

  p <- p %>%
    add_trace(y = NULL, x = NULL, mode = "markers", type = "scatter", marker = list(color = "blue"), name = "TleafEB") %>%
    add_trace(y = NULL, x = NULL, mode = "markers", type = "scatter", marker = list(color = "red"), name = "TleafCnd") %>%
    add_trace(y = NULL, x = NULL, mode = "markers", type = "scatter", marker = list(color = "green"), name = "Tair") %>%
    layout(
      legend = list(
        x = 0.9, y = 1,  
        bgcolor = "rgba(0,0,0,0)",  
        title = list(text = "")  
      )
    )
  p
})
```
**TleafEB:** leaf temperature deduced from energy balance.
**TleafCnd:** leaf temperature measured by thermocouple and used for gas exchange computations.

<!-- LEAK -->
```{r message=FALSE}
renderPlotly({
  par(mar = c(5.1, 4.1, 0, 1))
  p <- ggplot(data) +
    geom_point(aes_string(x = input$xcol1, y = data$Leak, color = "'Leakage from chamber'"), shape = 20) +
    theme_bw() +
    xlim(input$xmin, input$xmax) +
    ylab("µmol.m⁻².s⁻¹")

  p <- ggplotly(p)

  p <- p %>%
    add_trace(y = NULL, x = NULL, mode = "markers", type = "scatter", marker = list(color = "red"), name = "Leakage from chamber") %>%
    layout(
      legend = list(
        x = 0.9, y = 1,
        bgcolor = "rgba(0,0,0,0)",
        title = list(text = "")
      )
    )
  p
})



```

