---
title: "LI6800 output analysis"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    social: NULL
    source_code: NULL
    self_contained: TRUE
    theme: sandstone
runtime: shiny
---

```{r include=FALSE}
#Improvement Ideas
#Make it possible to directly fetch the file from LICOR instead of transferring
#Read fluo curves
```

```{r CHECK_LIBRARIES, message=FALSE, include=FALSE}
source("Required_libraries.R")
```

```{r DATA _SELECTION, message=FALSE, include=FALSE}
selected_file <- file.choose()
dateoffile <- readLines(selected_file, n=2)
date_line <- dateoffile[2]
date_string <- strsplit(date_line, "\t")[[1]][2]
file_date <- as.Date(date_string)

header_lines <- readLines(selected_file, n = 62)
data <- as.data.frame(read.delim(selected_file, header = FALSE, sep = "\t", skip = 64, fill = TRUE))
colnames(data) <- paste(data[1,])
data <- data[-c(1, 2), ]
columns_to_exclude <- c("time","date", "hhmmss", "averaging")
data <- data[, !colnames(data) %in% columns_to_exclude]
suppressWarnings(
  data[] <- lapply(data, as.numeric)
)
```



```{r TEST_FLUOFILES}
json_folder <- "C:\\Users\\lcta0001\\OneDrive - Sveriges lantbruksuniversitet\\Skrivbordet\\logs"
json_files <- list.files(json_folder, pattern = "\\.json$", full.names = TRUE)
extract_timestamp <- function(file_path) {
  # Read JSON file
  json_data <- fromJSON(file_path)
  
  # Extract timestamp value
  timestamp <- json_data$TIMESTAMP
  
  # Return timestamp value
  return(timestamp)
}
timestamps <- sapply(json_files, extract_timestamp)
print(timestamps)
```



Main_graph
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r X_AXIS, message=FALSE}

selectInput('xcol1',
            HTML('<span style="font-size: 16px;"><b>X  Axis Variable</b></span>'),
            choices = names(data))

sliderInput('xmin', 'X Min Value', min = min(data[[1]]), max = max(data[[1]]), value = min(data[[1]]))
sliderInput('xmax', 'X Max Value', min = min(data[[1]]), max = max(data[[1]]), value = max(data[[1]]))


observeEvent(input$xcol1, {
  updateSliderInput(session, 'xmin', 'X Min Value',
                    min = min(data[[input$xcol1]]),
                    max = max(data[[input$xcol1]]),
                    value = min(data[[input$xcol1]]))

  updateSliderInput(session, 'xmax', 'X Max Value',
                    min = min(data[[input$xcol1]]),
                    max = max(data[[input$xcol1]]),
                    value = max(data[[input$xcol1]]))
})
```



```{r Y_AXIS, message=FALSE}
    
selectInput('ycol1', 
            HTML('<span style="font-size: 16px;"><b>Y  Axis Variable</b></span>'), 
            names(data),
            selected=names(data)[[3]])

sliderInput('ymin', 'Y Min Value', min = min(data[[3]]), max = max(data[[3]]), value = min(data[[3]]))
sliderInput('ymax', 'Y Max Value', min = min(data[[3]]), max = max(data[[3]]), value = max(data[[3]]))


observeEvent(input$ycol1, {
  updateSliderInput(session, 'ymin', 'Y Min Value',
                    min = min(data[[input$ycol1]]),
                    max = max(data[[input$ycol1]]),
                    value = min(data[[input$ycol1]]))

  updateSliderInput(session, 'ymax', 'Y Max Value',
                    min = min(data[[input$ycol1]]),
                    max = max(data[[input$ycol1]]),
                    value = max(data[[input$ycol1]]))
})
```

```{r UNITS_BUTTON, message=FALSE}
actionButton("open_website", "LI-6800 summary of symbols")

observeEvent(input$open_website, {
  browseURL("https://www.licor.com/env/support/LI-6800/topics/symbols.html")
})

```

Column
-----------------------------------------------------------------------

```{r GRAPH, message=FALSE, warning=FALSE}
selectedData1 <- reactive(
  data[, c(input$xcol1, input$ycol1)],
)

renderPlotly({
  par(mar = c(5.1, 4.1, 0, 1))
  p <- ggplot(selectedData1(), aes_string(x=input$xcol1, y=input$ycol1)) +
    geom_point(shape=20) +
    theme_bw() +
    ylim(input$ymin, input$ymax) +
    xlim(input$xmin, input$xmax)
  
  ggplotly(p)
       })
```

If you want to download only the data used to generate this graph, press on the "Download" button below.
```{r DOWNLOAD_DATA, message=FALSE}
 downloadHandler(
   filename = function() {
       filename <- input$file$name
       paste(input$xcol1, input$ycol1, ".csv", sep = "_")
   },
   content = function(file) {
     data <- selectedData1()
     write.csv(data, file, row.names = FALSE)
   }
 )

 uiOutput("downloadButton")
```


```{r EXTRACT_DATA, message=FALSE}
column_selector <- tagList(
  checkboxInput("select_all_columns", "Show all parameters in the options", FALSE),
  selectInput(
    inputId = "columns",
    label = NULL,
    choices = c("obs", "elapsed", "E", "A", "Ci", "gsw", "Fo", "Fm", "Fv/Fm", "Fs", "Fm'","ETR"), 
    selected = NULL,
    multiple = TRUE
  )
)

observeEvent(input$select_all_columns, {
  if (input$select_all_columns) {
    updateSelectInput(session, "columns", choices = colnames(data))
  } else {
    updateSelectInput(session, "columns", choices = c("obs", "elapsed", "E", "A", "Ci", "gsw", "Fo", "Fm", "Fv/Fm", "Fs", "Fm'","ETR"))
  }
})

output$exported_data <- downloadHandler(
  filename = function() {
    paste("exported_data_", file_date, ".csv", sep = "")
  },
  content = function(file) {
    selected_data <- data[, input$columns, drop = FALSE]
    write.csv(selected_data, file, row.names = FALSE, sep = ",")
  }
)

tabPanel("Export Data",
         column(6,
                h3("Export Data"),
                column_selector,
                downloadButton("exported_data", "Download")
         )
)
```

Controls
=======================================================================

Row
-----------------------------------------------------------------------

<!-- TEMPERATURE -->
```{r message=FALSE, warning=FALSE}
# I should add stability criteria for instance?
palette <- brewer.pal(length(unique(data$CategoryVariable)), "Set1")

renderPlotly({
  par(mar = c(5.1, 4.1, 0, 1))
  p <- ggplot(data) +
    geom_point(aes_string(x = input$xcol1, y = data$TleafEB, color = "'TleafEB'"), shape = 20) +
    geom_point(aes_string(x = input$xcol1, y = data$TleafCnd, color = "'TleafCnd'"), shape = 20) +
    geom_point(aes_string(x = input$xcol1, y = data$Tair, color = "'Tair'"), shape = 20) +
    theme_bw() +
    xlim(input$xmin, input$xmax) +
    ylab("Temperature (°C)")

  p <- ggplotly(p)

  p <- p %>%
    add_trace(y = NULL, x = NULL, mode = "markers", type = "scatter", marker = list(color = "blue"), name = "TleafEB") %>%
    add_trace(y = NULL, x = NULL, mode = "markers", type = "scatter", marker = list(color = "red"), name = "TleafCnd") %>%
    add_trace(y = NULL, x = NULL, mode = "markers", type = "scatter", marker = list(color = "green"), name = "Tair") %>%
    layout(
      legend = list(
        x = 0.9, y = 1,  
        bgcolor = "rgba(0,0,0,0)",  
        title = list(text = "")  
      )
    )
  p
})
```
**TleafEB:** leaf temperature deduced from energy balance.
**TleafCnd:** leaf temperature measured by thermocouple and used for gas exchange computations.

<!-- LEAK -->
```{r message=FALSE, warning=FALSE}
renderPlotly({
  par(mar = c(5.1, 4.1, 0, 1))
  p <- ggplot(data) +
    geom_point(aes_string(x = input$xcol1, y = data$Leak, color = "'Leakage from chamber'"), shape = 20) +
    theme_bw() +
    xlim(input$xmin, input$xmax) +
    ylab("µmol.m⁻².s⁻¹")

  p <- ggplotly(p)

  p <- p %>%
    add_trace(y = NULL, x = NULL, mode = "markers", type = "scatter", marker = list(color = "red"), name = "Leakage from chamber") %>%
    layout(
      legend = list(
        x = 0.9, y = 1,
        bgcolor = "rgba(0,0,0,0)",
        title = list(text = "")
      )
    )
  p
})
```

Informations
=======================================================================

This part contains the header of your data. Important information to keep.


```{r HEADER, message=FALSE, results='asis'}
cat('<div style="overflow-y: scroll; max-height: calc(100vh - 150px);">')
print(header_lines)
cat('</div>')
```





